### 2021-12-03 text/outline/draft.tex
ensure up-to-date
change pair pod size to 200

\begin{document}
\noindent
Tim, Gene, Kathryn
\begin{center} 
\textbf{A class of exponential family measurement error models applied to single-cell CRISPR screens}
\end{center}

@@

We implement several statistical accelerations (that likely are of independent utility) to bring the cost of GLM-EIV down to within about an order of magnitude of the thresholding method. Finally, we develop a Docker-containerized application to deploy GLM-EIV at-scale across tens or hundreds of nodes on clouds (e.g., Microsoft Azure) and high-performance clusters. Leveraging this application, we apply GLM-EIV to analyze two recent, large-scale, high multiplicity-of-infection single-cell CRISPR screen datasets, yielding new biological and statistical insights.

@@

>>>>

\begin{document}
\noindent
Tim, Gene, Kathryn
\begin{center} 
\textbf{A class of exponential family measurement error models applied to CRISPR genome editing and single-cell sequencing}
\end{center}

@@

We implement several statistical accelerations (that possibly are independently useful) to bring the cost of GLM-EIV down to within about an order of magnitude of the thresholding method. Finally, we develop a Docker-containerized application to deploy GLM-EIV at-scale across tens or hundreds of nodes on clouds (e.g., Microsoft Azure) and high-performance clusters. Leveraging this application, we apply GLM-EIV to analyze two recent, large-scale, high multiplicity-of-infection single-cell CRISPR screen datasets, yielding new biological and statistical insights.

@@

% We anticipate three practical uses of the GLM-EIV in single-cell CRISPR screen analysis: first, determining the extent of background contamination, which will inform subsequent analysis decisions. Second, if the amount of background contamination is sufficiently high, thresholding will fail, and so GLM-EIV should be used to get a good answer. On the other hand, if the amount of background contamination is low, we would use the two methods in conjunction: first, fit GLM-EIV to some subset of the data (e.g., the positive control pairs) to get the approximate Bayes-optimal decision boundary; and second, using this decision boundary in the thresholding method. As we have shown, the threshold exerts a substantial impact on the results. In this way, GLM-EIV becomes a threshold selection procedure, enabling statistically rigorous and scientifically reproducible threshold selection procedure, eliminating the aribrariness of selecting a threshold by, for example, eye.
